The Deviation of China Map as a Regression Problem

### 2012-12-06 paper.tex
meh

Figure~\ref{fig:fxy-degree}(right) shows the plot where the deviation is
measured in meters.
It's a linear function, thus we can do a simple linear regression.
\begin{verbatim}
> dx=dx.*cos(y./180.*pi).*6371000.*pi./180;
> mx=[ones(size(y)),y]; std(mx*(pinv(mx)*dx)-dx)
ans =  0.14664
> pinv(mx)*dx
ans =
   406.3954
     2.5241
\end{verbatim}
The standard error, 0.14664 meters, is acceptable.
The final function is
\begin{equation}
f_x(110.16,y)=406.3954+2.5241y
\end{equation}
After trying out other constant longitudes,
we find out that the two coefficients are different for different longitude.
We have
\begin{equation}
f_x(x,y)=g_1(x)+g_2(x)\times y
\end{equation}
where $g_1(x)$ and $g_2(x)$ are not yet known.

@@

\section{The final 2D case: $f_x(x,y)$ and $f_y(x,y)$}
With out too much effort, we can find out the two functions:

\begin{eqnarray}
f_x(x,y) &=& 1598.1-23.605x -8.4345y +0.09933xy +0.10069x^2 \nonumber \\
          & & +199.1cos(\pi(x+0.017)/30) -99.772sin(\pi(x+0.0039)/12+\pi/4) \nonumber \\
          & & -26.687sin(\pi(x-0.0039)/3) -13.345sin(\pi(x-0.0039)) \nonumber \\
          & & +13.338sin(2\pi(x-0.0039)) +13.331sin(6\pi(x-0.0039)) \\
f_y(x,y) &=& -36.759 +1.5218x +10.002y -0.10032xy -0.03661y^2 \nonumber \\
         & & -217.44cos(\pi(y+8.143)/30)+106.41sin(\pi(y+1.1)/12) \nonumber \\
         & & -26.697sin(\pi(y+1)/3) +13.335sin(\pi y) \nonumber \\
         & & -13.329sin(2\pi(x-0.0039)) -13.319sin(6\pi(x-0.0039))
\end{eqnarray}
The standard errors are 0.43747 and 0.44031 meters respectively.

To verify the correctness, we can compute the deviated coordinates of Monument
to the People's Heroes given its true coordinates.

>>>>

Figure~\ref{fig:fxy-degree}(right) shows the plot where the deviation is
measured in meters.
It's a linear function, thus we can do a simple linear regression.
\begin{verbatim}
> dx=dx.*cos(y./180.*pi).*6371000.*pi./180;
> mx=[ones(size(y)),y]; std(mx*(pinv(mx)*dx)-dx)
ans =  0.14664
> pinv(mx)*dx
ans =
   406.3954
     2.5241
\end{verbatim}
The standard error, 0.14664 meter, is acceptable, because the input data's
resolution is about 0.6 meter\footnote{The input is converted from google map's
unit. One unit is one pixel under the maximum zoom setting. Due to Mercator
projection, higher latitude has higher resolution. The average 0.6 meter is
computed based on the mean coordinate, which is near Xi'an city.} on average.
The final function is
\begin{equation}
f_x(110.16,y)=406.3954+2.5241y
\end{equation}
After trying out other constant longitudes,
we find out that the two coefficients are different for different longitude.
We have
\begin{equation}
f_x(x,y)=g_1(x)+g_2(x)\times y
\label{eq:fxy}
\end{equation}
where $g_1(x)$ and $g_2(x)$ are not yet known.

@@

\section{The final 2D case: $f_x(x,y)$ and $f_y(x,y)$}

From Equation~\ref{eq:fxx} and \ref{eq:fxy} we know that $f_x(x,y)$ and
$f_y(x,y)$ must be in the following form.

\begin{eqnarray}
f_x(x,y) &=& a_1+a_2x+a_3y+a_4xy+a_5x^2 \nonumber \\
         & & +a_6sin(\pi x/30+b_1) +a_7sin(\pi x/12+b_2)+a_8sin(\pi x/3+b_3) \nonumber \\
         & & +a_9sin(\pi x+b_4)+a_{10}sin(2\pi x +b_5) +a_{11}sin(6\pi x+b_6) \\
f_y(x,y) &=& c_1 +c_2x +c_3y +c_4xy +c_5y^2 \nonumber \\
         & & +c_6sin(\pi y/30+d_1)+c_7sin(\pi y/12 +d_2)+c_8sin(\pi y/3+d_3) \nonumber \\
         & & +c_9sin(\pi y+d_4)+c_{10}sin(2\pi x+d_5) +c_{11}sin(6\pi x +d_6)
\end{eqnarray}

Applying the previous method on the data file \url{google-grid40.tsv}, we can
determine all the parameters easily.
The octave commands are skipped.
The resulting equations are shown below and their standard errors are 0.4373
and 0.43998 meters respectively.

\begin{eqnarray}
f_x(x,y) &=& 1596.7-23.578x -8.431y +0.0993xy +0.10056x^2 \nonumber \\
          & & -199.11sin(\pi x/30-1.5692) -99.77sin(\pi x/12+0.78662) \nonumber \\
          & & -26.687sin(\pi x/3-0.0040926) -13.344sin(\pi x-0.012222) \nonumber \\
          & & +13.338sin(2\pi x -0.024649) +13.331sin(6\pi x-0.073931) \\
f_y(x,y) &=& 42.304 -1.522x -10.376y +0.10032xy +0.041777y^2 \nonumber \\
         & & -217.35sin(\pi y/30 -0.71213)-106.38sin(\pi y/12 +0.28733) \nonumber \\
         & & +26.698sin(\pi y/3+1.0481) -13.335sin(\pi y+0.00012317) \nonumber \\
         & & +13.329sin(2\pi x-0.024639) +13.319sin(6\pi x -0.073933)
\end{eqnarray}

To verify their correctness, we can compute the deviated coordinates of Monument
to the People's Heroes using its true coordinates.
$f_x(116.391667,39.903056)=531.91$ meters and
$f_y(116.391667,39.903056)=155.39$ meters.
This means that the deviated coordinate is 531.91 meters to the east and 155.39
to the north, thus $x'=116.391667+531.91\times 360/(2\pi\times 6371000\times
cos(2\pi\times 39.903056/360))=116.397903$ and $y'=39.903056+155.39\times
360/(2\pi\times 6371000)=39.904453$.
We now put the deviated coordinate in a deviated map as in Figure~\ref{fig:map-jjmdd}.
It aligns nicely.
